Flexibility reduces social donations

### 2022-05-10 article-elsevier/article-elsevier.Rmd
cambios en ETL para replicar

#### Pannel data regression

We want to study the effect on donations of the change of law of 20.565 to 20.900, the main change is that for the law 20.900 is no longer necessary to donor to at least two different institution an amount minor to 700 UTM (in Section XX number XX) making more easy to receive the economy incentive for donation, in order to that, is it expected that the donations raise (in number) but we don't now for sure what happens with the amount of the donations

We use a pannel data regression in order to study the effect of the change of law on the donations, and follow the next pannel structure

>>>>

#### Panel data regression

We want to study the effect on donations of the change of law of 20.565 to 20.900, the main change is that for the law 20.900 is no longer necessary to donor to at least two different institution an amount minor to 700 UTM (in Section XX number XX) making more easy to receive the economy incentive for donation, in order to that, is it expected that the donations raise (in number) but we don't now for sure what happens with the amount of the donation.

We use a panel data regression in order to study the effect of the change of law on the donations, and follow the next pannel structure:
